Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
foo

\usepackage{url}

@@

A key goal in improving patient-clinician communication is
establishing a common context for communication with which a shared
understanding can be established.  This understanding is
bi-directional, in the sense that, both the patient needs to be able
to properly interpret what the clincian is trying to convey to him or
her, while the clinician needs to be able to arrive at an accurate
characterisation of the patient's situation, as updated since the last
time he or she met with the patient.

One of the most promising technologies to help provide a common
context of communication is the patient-centric electronic health
record\cite{ehr} which constitute a complete medical history of
a patient as recorded through his or her entire life. (...)

@@

\section{Personal Electronic Sensors}

There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.

The measurements from such devices are of particular interest because of the
frequency and granularity of measurement that they perform - showing minute-by-minute updates
throughout the day, with no clinical involvement.

In addition to fitness monitors, the market for quantified self sensors has
expanded into areas of personal health. For example, there are sensors for
measuring blood oxygenation~\footnote{SpO2 Blood Oxygenation sensor: \url{http://ispo2.com}},
Heart Rate Variability and Respiratory Rate~\footnote{Zensorium Tinke, heart and respiratory rate sensor: \url{http://www.zensorium.com/tinke/}} and
Temperature and Galvanic Skin Response~\footnote{BodyMedia Core 2, temperature and GSR sensor: \url{http://www.bodymedia.com}}.
There is even a wireless fork that informs you how long you spent eating~\footnote{HapiLabs HapiFork: \url{http://hapilabs.com/products-hapifork.asp}}.

>>>>

@@

A key goal in improving patient-clinician communication is
establishing a common context for communication with which a shared
understanding can be established.  This understanding is
bi-directional, in the sense that the patient needs to be able to
effectively interpret what the clincian is trying to convey to him or
her, but also the clinician needs to be able to arrive at an accurate
characterisation of the patient's situation (often under time
constraints) as updated since the last time the clinician met with the
patient.

One of the most promising technologies that has the potential to help
provide such a common context is the patient-centric electronic health
record (henceforth EHR)\cite{ehr}, a digital representation of the
complete medical history of an individual as recorded by clinicians
throughout a patient's life. The EHR promises to enable both
patients and their clinicians unfettered access to the patient's
medical data, including diagnostics, reports, and history of
interventions.  This means that clinicians can more easily review a
patient's long-term history in the course of basing interpretations
and interventions. Moreover, since patients have access to their own
medical histories, there is (theoretically) a basis by which patients
can understand the justifications for clinicial prognoses.

% proactive activity recording to provide sketches of a person's
% activity profiles outside of the hospital, streaming data

Yet so far, the ``medical history'' that EHRs have been used to store
have constituted only the official diagnoses and diagnostic reports
prepared by clinicians, technicians and nurses

@@
